---
title: "p8105_hw6_kx2173"
author: "Ke Xu"
date: "12/4/2021"
output: html_document
---

```{r}
library(tidyverse)
library(modelr)
library(purrr)
library(mgcv)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


# Problem 1

Load and clean the data for regression analysis.
```{r}
birthweight_df = read.csv("birthweight_data/birthweight.csv") %>% 
  janitor::clean_names()

# Check missing value
sum(is.na(birthweight_df))

birthweight_df = birthweight_df %>% 
  mutate(
    babysex = factor(babysex, ordered = FALSE),
    frace = factor(frace, ordered = FALSE),
    malform = factor(malform, ordered = FALSE),
    mrace = factor(mrace, ordered = FALSE)
  )
```

Propose a regression model for birthweight.
```{r}
model_1 = lm(bwt ~ ppbmi + delwt, data = birthweight_df) 

model_1 %>% broom::tidy()

plot = birthweight_df %>% 
  add_residuals(model_1) %>% 
  add_predictions(model_1) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point(alpha = 0.5) +
  geom_abline(slope = 0, intercept = 0, color = "red") +
  labs(
    title = "Residuals vs Fitted value Plot",
    x = "Fitted value",
    y = "Residuals"
  ) +
  theme(plot.title = element_text(hjust = 0.5))

```

Describe modeling process:
1. Firstly, load and clean data;
2. Then I think "mother's weight at delivery (pounds)" and "mother's pre-pregnancy BMI" my influence baby's birth weight, so I use these two variables as the predictors of the model;
3. Then I drew a "Residuals vs Fitted value Plot". From the plot, residual values are bounce around 0, which means they are evenly distributed around 0. Therefore, it is a reasonable model and I keep this model.


Compare your model to two others:
```{r}
model_2 = lm(bwt ~ blength + gaweeks, data = birthweight_df)
model_3 = lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = birthweight_df)

cv_df = crossv_mc(birthweight_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)) %>% 
  mutate(
    mod_1 = map(.x = train, ~lm(bwt ~ ppbmi + delwt, data = .x)),
    mod_2 = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    mod_3 = map(.x = train, ~lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = .x))) %>% 
  mutate(
    rmse_1 = map2_dbl(.x = mod_1, .y = test, ~rmse(model = .x, data = .y)),
    rmse_2 = map2_dbl(.x = mod_2, .y = test, ~rmse(model = .x, data = .y)),
    rmse_3 = map2_dbl(.x = mod_3, .y = test, ~rmse(model = .x, data = .y))) %>%
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin() +
  labs(title = "RMSEs for Each Model",
       x = "Model",
       y = "RMSE") +
  theme(plot.title = element_text(hjust = 0.5))
```

















