---
title: "p8105_hw6_kx2173"
author: "Ke Xu"
date: "12/4/2021"
output: html_document
---

```{r}
library(tidyverse)
library(modelr)
library(purrr)
library(patchwork)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

#### Load and clean the data for regression analysis.
```{r}
birthweight_df = read.csv("birthweight_data/birthweight.csv") %>% 
  janitor::clean_names()

# Check missing value
sum(is.na(birthweight_df))

birthweight_df = birthweight_df %>% 
  mutate(
    babysex = factor(babysex, ordered = FALSE),
    frace = factor(frace, ordered = FALSE),
    malform = factor(malform, ordered = FALSE),
    mrace = factor(mrace, ordered = FALSE)
  )
```

#### Propose a regression model for birthweight.
```{r}
model_1 = lm(bwt ~ ppbmi + delwt, data = birthweight_df) 

model_1 %>% broom::tidy()

plot = birthweight_df %>% 
  add_residuals(model_1) %>% 
  add_predictions(model_1) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point(alpha = 0.5) +
  geom_abline(slope = 0, intercept = 0, color = "red") +
  labs(
    title = "Residuals vs Fitted value Plot",
    x = "Fitted value",
    y = "Residuals"
  ) +
  theme(plot.title = element_text(hjust = 0.5))

```

Describe modeling process:
1. Firstly, load and clean data;
2. Then I think "mother's weight at delivery (pounds)" and "mother's pre-pregnancy BMI" my influence baby's birth weight, so I use these two variables as the predictors of the model;
3. Then I drew a "Residuals vs Fitted value Plot". From the plot, residual values are bounce around 0, which means they are evenly distributed around 0. Therefore, it is a reasonable model and I keep this model.


#### Compare your model to two others:
```{r}
model_2 = lm(bwt ~ blength + gaweeks, data = birthweight_df)
model_3 = lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = birthweight_df)

cv_df = crossv_mc(birthweight_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)) %>% 
  mutate(
    mod_1 = map(.x = train, ~lm(bwt ~ ppbmi + delwt, data = .x)),
    mod_2 = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    mod_3 = map(.x = train, ~lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = .x))) %>% 
  mutate(
    rmse_1 = map2_dbl(.x = mod_1, .y = test, ~rmse(model = .x, data = .y)),
    rmse_2 = map2_dbl(.x = mod_2, .y = test, ~rmse(model = .x, data = .y)),
    rmse_3 = map2_dbl(.x = mod_3, .y = test, ~rmse(model = .x, data = .y))) %>%
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin() +
  labs(title = "RMSEs for Each Model",
       x = "Model",
       y = "RMSE") +
  theme(plot.title = element_text(hjust = 0.5))
```
Based on the violin plot, we can find that model 1 has a higher error rate than the other two models and model 3 has the smallest RMSE value. Model 3 is more accurate than model 1 and model 2.


## Problem 2

#### Load 2017 Central Park weather data
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

#### Use 5,000 bootstrap samples:

Distribution of $\hat{r}^2$
```{r}
bootstrap_rsquared = weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::glance)) %>%
  select(-strap, -models) %>% 
  unnest(results) %>% 
  select(.id, r.squared)

plot_rsquared = bootstrap_rsquared %>% 
  ggplot(aes(x = r.squared)) +
  geom_density(color = "chocolate1") +
  labs(
    title = "R-squared Distribution by Bootstrap",
    x = "R Squared",
    y = "Density") +
  theme(plot.title = element_text(hjust = 0.5))

plot_rsquared
```

Distribution of $log(\hat{\beta}_0 \ast \hat{\beta}_1)$
```{r}
bootstrap_logbeta = weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::tidy)) %>%
  unnest(results) %>% 
  select(.id, term, estimate) %>% 
  mutate(term = recode(term, `(Intercept)` = "beta0_hat", `tmin` = "beta1_hat")) %>%
  pivot_wider(
    names_from = "term",
    values_from = "estimate") %>% 
  mutate(log_beta01 = log(beta0_hat * beta1_hat))

plot_logbeta = bootstrap_logbeta %>% 
  ggplot(aes(x = log_beta01)) +
  geom_density(color = "chocolate1") +
  labs(
    title = "Log_beta Distribution by Bootstrap",
    x = "Log(β0 * β1)",
    y = "Density") +
  theme(plot.title = element_text(hjust = 0.5))

plot_logbeta
```

Describe the distribution of estimates:
From these two plots, we can find that both r-squared and log(β0 * β1) are approximately normal distributed. The highest density value for r-squared is between 0.91 and 0.92, which is close to 1 so the data is well fitted with the regression model. The highest density value for log(β0 * β1) is between 2.00 and 2.025.


#### Provide 95% confidence interval for the estimates
```{r}
# R-squared confidence interval
ci_rsquared = bootstrap_rsquared %>% 
  summarise(
    ci_lower = quantile(r.squared, 0.025), 
    ci_upper = quantile(r.squared, 0.975)) %>% 
  knitr::kable(caption = "95% CI for R-squared", digits = 2)

ci_rsquared

# Log_beta confidence interval
ci_logbeta = bootstrap_logbeta %>% 
  summarise(
    ci_lower = quantile(log_beta01, 0.025), 
    ci_upper = quantile(log_beta01, 0.975)) %>% 
  knitr::kable(caption = "95% CI for Log_beta", digits = 2)

ci_logbeta
```















